The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
methods

Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another. Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al. 2019). Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.

>>>>

Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another. Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al. 2019). Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented connections between the same individuals across contexts.
